Model Search in Relational Domains

### 2016-10-22 graphs.tex
caps
caption

%%%%%%%%%%%%%%%%%%%%%%%%%% scatter plots %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{tabular}{@{\hspace{-1.5em}}c@{\hspace{1em}}c}
\begin{tikzpicture}[scale=0.75]
	\begin{loglogaxis} [xmin=0.1,xmax=4000, ymin=0.1, ymax=4000, xlabel= SAT (decision),
			ylabel=ACDCL (decision), 
			legend pos = north west,
			%legend style={at={(0.8,0.15)},
			%anchor=north,legend columns=-1 },
			]
\addplot [mark size=1pt,only marks,scatter,point meta=explicit symbolic,
	scatter/classes={s={mark=square},u={mark=triangle*,blue}},] 
	table [meta=label] {plotdata/scatter-decision.dat};
	\legend{Safe,Unsafe}
\addplot [domain=.1:4000] {x};
%\addplot [red,sharp plot, domain=.1:1500] {900}
%          node [below] at (axis cs:10,850) {timeout};
%\addplot [red,sharp plot, domain=.1:1500] coordinates{(900,.1) (900,1500)}
%          node [left,rotate=90] at (axis cs:700,10) {timeout}
 %node [right,black] at (axis cs:10,3) {portfolio faster}
 %node [right,black] at (axis cs:1,55) {kIkI faster};
%\addplot [red,sharp plot, update limits=false] coordinates{(900,.1) (900,1500)}
%	node [left] at {axis cs:700,200} {timeout};
\end{loglogaxis}
\end{tikzpicture}
 &
\begin{tikzpicture}[scale=0.75]
	\begin{loglogaxis} [xmin=.1,xmax=83000, ymin=.1, ymax=83000, xlabel=SAT (Propagation),
			ylabel=ACDCL (Propagation),
			legend pos = north west,
      %legend style={at={(0.8,0.15)},
			%anchor=north,legend columns=-1 },
			]
\addplot [mark size=1pt,only marks,scatter,point meta=explicit symbolic,
	scatter/classes={s={mark=square},u={mark=triangle*,blue}},] 
	table [meta=label] {plotdata/scatter-propagation.dat};
	\legend{Safe,Unsafe}
\addplot [domain=.1:83000] {x};
%\addplot [red,sharp plot, domain=.1:1500] {900}
%          node [below] at (axis cs:10,850) {timeout};
%\addplot [red,sharp plot, domain=.1:1500] coordinates{(900,.1) (900,1500)}
%          node [left,rotate=90] at (axis cs:700,150) {timeout}
 %node [right,black] at (axis cs:10,3) {CPAchecker faster}
 %node [right,black] at (axis cs:1,55) {kIkI faster};
\end{loglogaxis}
\end{tikzpicture} \\
(a) & (b)
\end{tabular}
\caption{\label{fig:results}
Comparison between SAT and ACDCL 
}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%% scatter plots %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{tabular}{@{\hspace{-1.5em}}c@{\hspace{1em}}c}
\begin{tikzpicture}[scale=0.75]
	\begin{loglogaxis} [xmin=0.1,xmax=4000, ymin=0.1, ymax=4000, xlabel= SAT (Decision),
			ylabel=ACDCL (Decision), 
			legend pos = north west,
			%legend style={at={(0.8,0.15)},
			%anchor=north,legend columns=-1 },
			]
\addplot [mark size=1pt,only marks,scatter,point meta=explicit symbolic,
	scatter/classes={s={mark=square},u={mark=triangle*,blue}},] 
	table [meta=label] {plotdata/scatter-decision.dat};
	\legend{Safe,Unsafe}
\addplot [domain=.1:4000] {x};
%\addplot [red,sharp plot, domain=.1:1500] {900}
%          node [below] at (axis cs:10,850) {timeout};
%\addplot [red,sharp plot, domain=.1:1500] coordinates{(900,.1) (900,1500)}
%          node [left,rotate=90] at (axis cs:700,10) {timeout}
 %node [right,black] at (axis cs:10,3) {portfolio faster}
 %node [right,black] at (axis cs:1,55) {kIkI faster};
%\addplot [red,sharp plot, update limits=false] coordinates{(900,.1) (900,1500)}
%	node [left] at {axis cs:700,200} {timeout};
\end{loglogaxis}
\end{tikzpicture}
 &
\begin{tikzpicture}[scale=0.75]
	\begin{loglogaxis} [xmin=.1,xmax=83000, ymin=.1, ymax=83000, xlabel=SAT (Propagation),
			ylabel=ACDCL (Propagation),
			legend pos = north west,
      %legend style={at={(0.8,0.15)},
			%anchor=north,legend columns=-1 },
			]
\addplot [mark size=1pt,only marks,scatter,point meta=explicit symbolic,
	scatter/classes={s={mark=square},u={mark=triangle*,blue}},] 
	table [meta=label] {plotdata/scatter-propagation.dat};
	\legend{Safe,Unsafe}
\addplot [domain=.1:83000] {x};
%\addplot [red,sharp plot, domain=.1:1500] {900}
%          node [below] at (axis cs:10,850) {timeout};
%\addplot [red,sharp plot, domain=.1:1500] coordinates{(900,.1) (900,1500)}
%          node [left,rotate=90] at (axis cs:700,150) {timeout}
 %node [right,black] at (axis cs:10,3) {CPAchecker faster}
 %node [right,black] at (axis cs:1,55) {kIkI faster};
\end{loglogaxis}
\end{tikzpicture} \\
(a) & (b)
\end{tabular}
\caption{\label{fig:results}
Comparison of the number of decisions and propagations performed by
propositional SAT and ACDCL}
\end{figure}
